Airline Customer Satisfaction - Group 17

### 2025-03-27 Draft Business Analytics Assignment Group 17.Rmd
Updated Chapter 1

@@

>>>>

In this project, Group 17 serves as business consultants, with a focus on improving customer experience in the industry. Our responsibilities are from analyzing customer satisfaction statistics, developing measures to improve the airline's overall performance. Therefore, the business problem that we solve is "how the airline can improve its strategy of services and activities to significantly increase customer satisfaction, especially between segments and main service areas, thus promoting customer loyalty and achieving stronger competitive advantages?".

**The reason why we chose airline industry as our focus :**

* We provide comprehensive data from Kaggle across various aspects of the flying experience which allows us to in-depth analysis.

* Intense rivalry airline industry has intense competition among company, and it could be easily justified by customer satisfaction. Thus, higher customer satisfaction leads to increased client retention and overall business performance.

* Concentrating on major market segments may be an efficient technique for improving overall consumer satisfaction.

**Why focus on customer satisfaction?**

Enhance customer loyalty: improving on these key segments and service areas will enhance customer satisfaction that potentially increases customer loyalty rate.

Competitive Advantage: by addressing the service issue, the airline can stand out from the competitors.

@@

Lorem IpsumBesides the Basic R Functions, this  project uses multiple packages to enhance the R functionalities and improve the data analytics and visualization quality. This section explains all the packages and functions beyond the Basic R functionalities that we are using in this project in each step of the business analytics process from data cleaning to modeling.

* Data Cleaning

**dplyr** : used to filter rows, select columns, sort data, create new columns, and summarize data.

* Data Exploration

**skimr** : designed to provide summary of statistical measures for each variables in data frames.
**DataExplorer** : used to display comprehensive and convenient interface for data exploration and data visualization.

* Data Preparation

* Data Transformation

* Data Visualization

**ggplot2** : a package that is useful to visualize data in a more complex and customizable way compared to the basic R plotting functions.

* Data Modeling

* Data Analysis

Below we will find the commands to install and import the required libraries:
